---
title: "R Assignment"
output: pdf_document
date: '2022-04-08'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
Dataset<- read.csv(file.choose())
```

#Printing structure
```{r}
str(Dataset)
```

#List of Varibles 
```{r}
 list(Dataset)
```

#Print top 15 rows of dataset
```{r}
  head(Dataset, 15) 
```

#One user defined function
```{r}
  max(Dataset$Total)
 
  Dataset$X1980 > Dataset$X1981

```

#Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset
## R Markdown
```{r}
  library("dplyr")
  
    library("tidyverse")
   
   IndiaImmgration<- filter(as.data.frame(Dataset%>% select(1,5,38)),Country=="India")
   
   IndiaImmgration

```

#Remove Missing Values 
```{r}
   is.na(Dataset)
   
   na.omit(Dataset)

```

#Identify and remove duplicate data from your data set
```{r}
   SampleDuplicate<- c(1,1,2,3,4,1,5,6)
   
   SampleDuplicate
   
   duplicated(SampleDuplicate)
     
    SampleDuplicate[duplicated(SampleDuplicate)]
    SampleDuplicate[!duplicated(SampleDuplicate)]

```

#Reorder multiple rows in descending order.
```{r}
    library(dplyr)
    
    Dataset%>%arrange(desc(X2001), desc(X2002))

```

#Rename Coloumns
```{r}
names(Dataset)[2]= "Continent1"
```

#Add new variables in your data frame by using a mathematical function
```{r}
Dataset%>%mutate(newTotal=Total*2)
```

#Create a training set using random number generator engine.
```{r}
    (N <- nrow(Dataset))
    
   (target <- round(N*0.80))
   
   gp <- runif(N)
   
   Dataset_train <- Dataset[gp< 0.80,]
   
   nrow(Dataset_train)

```

#Print the summary statistics of your dataset
```{r}
   summary(Dataset)
   
   Dataset%>%group_by(Total)%>%summarise(mean(Total))

```

#Use any of the numerical variables from the dataset and perform the following statistical functions
```{r}
   mean(Dataset$Total)
   
   median(Dataset$Total)
   
   mode(Dataset$Total)
   
   range(Dataset$Total)

```

#Plot a scatter plot for any 2 variables in your dataset  
```{r}
 
  ggplot(data = Dataset, 
         aes(x=Continent1, y=X2013, colour=X2013)) +
     geom_point()

```

#Plot a bar plot for any 2 variables in your dataset
```{r}
  ggplot(data = Dataset, 
         aes( x=DevName, fill= factor(Dataset$Continent))) +
     geom_bar()

```

#Find the correlation between any 2 variables by applying least square linear regression model
```{r}
   X= Dataset$Total
   Y= Dataset$X2013
   xycorr= cor(Y,X,method = "pearson")
   xycorr

```



